Oregon_Wildfire_full

### 2017-03-08 r_scripts/oregon_clean.rmd
Path to read excel file for place of service code was redefined
Update oregon_clean.rmd
change to right density plot

read_path <- paste0("../../../data/data_original/gan_episodes_of_care.txt")

# import the full dataframe, change column class to character
read_path <- paste0("../data/gan_episodes_of_care.txt")
start_time <- Sys.time()
oregon_df <- fread(read_path, sep = "|", showProgress = T, 
                   colClasses = rep("character", 72)) 
stop_time <-  Sys.time() - start_time 
# time it took
stop_time # about 20 mins

@@

hist(visit3$num_visit, freq = T, xlab = "number of visit", main = "Visiting number for each personkey")

@@

### Output html?

>>>>

read_path <- paste0("../../../data/data_original/gan_episodes_of_care.txt")
start_time <- Sys.time()
oregon_df <- fread(read_path, sep = "|", showProgress = T, 
                   colClasses = rep("character", 72)) 
stop_time <-  Sys.time() - start_time 
# time it took
stop_time # about 20 mins

@@

ggplot(visit3, aes(n)) + geom_density()

@@
